\vspace*{-2.5cm} \hspace*{-0.5cm}Online platformazation and Offline expansion of Real Estate Brokerage: Evidence from China\footnote{ We are grateful for various people from various university, and several conferences for useful feedback. }

### 2024-07-04 manuscript/main.tex
modified:   manuscript/main.aux 	modified:   manuscript/main.fdb_latexmk 	modified:   manuscript/main.log 	modified:   manuscript/main.pdf 	modified:   manuscript/main.synctex.gz 	modified:   manuscript/main.tex

From the graph, we can see that the

>>>>

% 从图中，我们可以发现大多数的节点都是相互连接的，但是部分节点是与其他节点互不相连的，这一方面说明了，对于部分局部市场，链家拥有的网络效应并不是很强，也证明了链家的网络更类似于局部的clustering而不是整体相连；另一方面，对于最大的connected component，节点的分布也具有不对称性，可以看到部分门店具有中心作用，其拥有更大的网络可达性，而部分节点虽然与其他节点相连，但是其更多的是处于局部小三角，小聚合，所以其网络效应不大。最后，我们可以发现，对于门店节点所连接的其他neighborhood节点，其分布也不具备对称性，对于高聚合度的门店节点其拥有的neighborhood节点也更为密集，这一方面是因为其具有更高的经济价值，所以其在网络中的地位也更高，所以其拥有的网络效应也更强。最后，综合来看

From the figure, we can observe that most nodes are interconnected, but some nodes are not connected to others. This indicates that, in certain local markets, Lianjia's network effect is not very strong, demonstrating that Lianjia's network is more akin to localized clustering rather than being entirely interconnected. On the other hand, for the largest connected component, the distribution of nodes is also asymmetric. Some stores play a central role, possessing greater network accessibility, while other nodes, although connected to others, are more likely to form small local triangles or clusters, resulting in a smaller network effect. Finally, we can observe that the distribution of neighborhood nodes connected to store nodes is also asymmetrical. Stores with higher aggregation degrees have denser neighborhood nodes, partly due to their higher economic value, which enhances their status in the network and strengthens their network effect. Overall, these observations suggest that while Lianjia's network exhibits significant local clustering, its overall network connectivity varies, with certain stores and neighborhoods playing pivotal roles due to their higher economic significance. The stronger network effects observed in high-value areas emphasize the role of economic factors in shaping the structure and influence of the network.
